### 2023-01-30 paper-thesis/chapters/40-discussing-statix.tex
Cleanup work
Ok this is already a thing

\chapter{Ergonomics of Spoofax}

@@

	\item Generic constraints. For example, we created two separate relations for reversing lists of different types, making these one generic function would've been better. This was the only case where this feature would've been useful for this thesis, but it may be more useful for other work.

	\item A better way to control the errors generated by Statix, such that users of the language get good errors. Statix does support \texttt{expr | error "Error text here"} annotations, but these don't allow constraints that instantiate metavariables on the left hand side whereas this would be needed for good error messages for dependently typed languages, since \verb|expectBetaEq| may infer variables. \todo{This is not true}
\end{enumerate}

>>>>

\chapter{Ergonomics of Spoofax}
\label{ch:ergonomics}

@@

	\item Generic constraints. For example, we created two separate relations for reversing lists of different types, making these one generic function would've been better. This was the only case where this feature would've been useful for this thesis, but it may be more useful for other work.
\end{enumerate}
